### 2017-04-30 paper/jfp-submission/locating.tex
minor

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of student programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, around 15\% for each tool, leaving us with a benchmark set of
1,569 programs.

\paragraph{Threats to Validity}
Our benchmarks were drawn from students in an undergraduate course
at \ucsdbench\ and may not be representative of other student bodies.
%
We mitigate this threat with a large empirical evaluation of 1,569
programs, drawn from a cohort of 46 students.
%
A similar threat is that students are not industrial programmers, thus
our results may not translate to large-scale software engineering.
%
In particular, \toolname's reliance on running the program suggests that
scaling it to larger programs would be more difficult than static
methods.
%
However, in our experience programmers are able to construct a mental
model of type systems after sufficient exposure, at which point
traditional error reports may suffice.
%
We are thus particularly interested in aiding novice programmers as
they learn to work with the type system.

>>>>

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, around 15\% for each tool, leaving us with a benchmark set of
1,569 programs.

\paragraph{Threats to Validity}
Our benchmarks were drawn from students in an undergraduate course
at \ucsdbench\ and may not be representative of other student bodies.
%
We mitigate this threat with a large empirical evaluation of 1,569
programs, drawn from a cohort of 46 students.
%
A similar threat is that students are not industrial programmers, thus
our results may not translate to large-scale software engineering.
%
% In particular, \toolname's reliance on running the program suggests that
% scaling it to larger programs would be more difficult than static
% methods.
%
However, in our experience programmers are able to construct a mental
model of type systems after sufficient exposure, at which point
traditional error reports may suffice.
%
We are thus particularly interested in aiding novice programmers as
they learn to work with the type system.
